---
title: 'repro'
output:
  html_document:
    toc: true
---


# Summary

times_sw1_seas and times_sw1+2_ann are best. 

## sw1_seas

No non-0 non-interaction coefs. 

log_size:temp_wet_t_1 `--`, log_size:prec_dry_t_1 `---`, log_size:prec_wet_t_1 `++`, log_size:sw1_dry_t_1 `+++`, log_size:sw1_wet_t_1 `--`.

## sw2_ann

no non-0 non-interaction coefs. 

log_size:seas_temp_t_1 `++` (but possibly 0), log_size:total_prec_t_1 `++` (but possible 0), log_size:seas_prec_t_1 `++`, seas_sw2_t_1 `--`. 

## sw1_ann

no non-0 non-interaction coefs. 

log_size:seas_prec_t_1 `++`, log_size:mean_sw1_t_1 `+` (but possible 0). 

## Overall

I ike that the precipitation seasonality coefficients line up with the seasonal model precipitation coefficients. This feels right. Seasonality in soil moisture doesn't appear to carry over. However, there is a strong effect in the seasonal model, which I tend to weight more evidence for given the WAIC result.

# All Results

```{r echo = FALSE}

 mod_list <- readRDS('../../Model_Fits/ramet_repro_list_krig.rds') 
```

## WAIC Results

```{r echo = FALSE}

 print(mod_list[[1]]$mod_waic.diffs) 

```

##  native_only   

```{r echo = FALSE}

 summary(mod_list[[1]][[1]], prob = 0.89) 

 plot(mod_list[[1]][[1]], ask = FALSE)
 pp_check(mod_list[[1]][[1]],
type   = 'bars_grouped',
group  = 'site',
freq   = FALSE,
ndraws = 100L) 

```



##  add_sw1_seas   

```{r echo = FALSE}

 summary(mod_list[[1]][[2]], prob = 0.89) 

 plot(mod_list[[1]][[2]], ask = FALSE)
 pp_check(mod_list[[1]][[2]],
type   = 'bars_grouped',
group  = 'site',
freq   = FALSE,
ndraws = 100L) 

```



##  times_sw1_seas   

```{r echo = FALSE}

 summary(mod_list[[1]][[3]], prob = 0.89) 

 plot(mod_list[[1]][[3]], ask = FALSE)
 pp_check(mod_list[[1]][[3]],
type   = 'bars_grouped',
group  = 'site',
freq   = FALSE,
ndraws = 100L) 

```



##  add_sw2_seas   

```{r echo = FALSE}

 summary(mod_list[[1]][[4]], prob = 0.89) 

 plot(mod_list[[1]][[4]], ask = FALSE)
 pp_check(mod_list[[1]][[4]],
type   = 'bars_grouped',
group  = 'site',
freq   = FALSE,
ndraws = 100L) 

```



##  times_sw2_seas   

```{r echo = FALSE}

 summary(mod_list[[1]][[5]], prob = 0.89) 

 plot(mod_list[[1]][[5]], ask = FALSE)
 pp_check(mod_list[[1]][[5]],
type   = 'bars_grouped',
group  = 'site',
freq   = FALSE,
ndraws = 100L) 

```



##  add_Sw3_seas   

```{r echo = FALSE}

 summary(mod_list[[1]][[6]], prob = 0.89) 

 plot(mod_list[[1]][[6]], ask = FALSE)
 pp_check(mod_list[[1]][[6]],
type   = 'bars_grouped',
group  = 'site',
freq   = FALSE,
ndraws = 100L) 

```



##  times_sw3_seas   

```{r echo = FALSE}

 summary(mod_list[[1]][[7]], prob = 0.89) 

 plot(mod_list[[1]][[7]], ask = FALSE)
 pp_check(mod_list[[1]][[7]],
type   = 'bars_grouped',
group  = 'site',
freq   = FALSE,
ndraws = 100L) 

```



##  add_sw1_ann   

```{r echo = FALSE}

 summary(mod_list[[1]][[8]], prob = 0.89) 

 plot(mod_list[[1]][[8]], ask = FALSE)
 pp_check(mod_list[[1]][[8]],
type   = 'bars_grouped',
group  = 'site',
freq   = FALSE,
ndraws = 100L) 

```



##  times_sw1_ann   

```{r echo = FALSE}

 summary(mod_list[[1]][[9]], prob = 0.89) 

 plot(mod_list[[1]][[9]], ask = FALSE)
 pp_check(mod_list[[1]][[9]],
type   = 'bars_grouped',
group  = 'site',
freq   = FALSE,
ndraws = 100L) 

```



##  add_sw2_ann   

```{r echo = FALSE}

 summary(mod_list[[1]][[10]], prob = 0.89) 

 plot(mod_list[[1]][[10]], ask = FALSE)
 pp_check(mod_list[[1]][[10]],
type   = 'bars_grouped',
group  = 'site',
freq   = FALSE,
ndraws = 100L) 

```



##  times_sw2_ann   

```{r echo = FALSE}

 summary(mod_list[[1]][[11]], prob = 0.89) 

 plot(mod_list[[1]][[11]], ask = FALSE)
 pp_check(mod_list[[1]][[11]],
type   = 'bars_grouped',
group  = 'site',
freq   = FALSE,
ndraws = 100L) 

```



##  add_Sw3_ann   

```{r echo = FALSE}

 summary(mod_list[[1]][[12]], prob = 0.89) 

 plot(mod_list[[1]][[12]], ask = FALSE)
 pp_check(mod_list[[1]][[12]],
type   = 'bars_grouped',
group  = 'site',
freq   = FALSE,
ndraws = 100L) 

```



##  times_sw3_ann   

```{r echo = FALSE}

 summary(mod_list[[1]][[13]], prob = 0.89) 

 plot(mod_list[[1]][[13]], ask = FALSE)
 pp_check(mod_list[[1]][[13]],
type   = 'bars_grouped',
group  = 'site',
freq   = FALSE,
ndraws = 100L) 

```

