---
title: "Appendix functions"
author: "Sam Levin, Ana Bogdan"
date: "8/8/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

## Drone results

The drone surveys from 2018 required 6 batteries over the course of 2 days due to a limited battery supply. Ambient temperature was approximately 24 degrees and there were no clouds present during either sampling period. In total, 1720 images were taken of the population from a height of ~9m above ground level. Due to difficulties in following the terrain perfectly, pixel sizes varied, though were on average 0.26cm/pixel. Pix4DMapper successfully geolocated and matched 1695/1720 images across 6 blocks, with a median of 10005.9 matches/image and a 1.83% difference in initial and optimized camera parameters. 

The 2019 survey was conducted on a single day under similar conditions to 2018. 1024 images were collected 10-15m above ground level to increase the variability within each image and prevent Pix4DMapper from generating blocks during orthomosaic generation. 1021/1024 images were successfully calibrated in a single block with a mean resolution of 0.45cm/pixel. Despite the drop in resolution, flowers and plants were still quite easy to identify in the resulting orthomosaic. Images had a median of 10219.3 matches, and there was a 0.35% difference between initial and optimized camera parameters. 

```{r setup, echo = FALSE}

knitr::opts_knit$set(root.dir = '../../../carpobrotus_IPMs')

```

```{r echo = FALSE, include = FALSE, cache = TRUE}

source('Ana_Israel_IPM/R/01_Utility_Functions_and_Dependencies.R')
source('Ana_Israel_IPM/R/02_Read_Data.R')
source('Ana_Israel_IPM/R/03_VR_Model_Selection.R')
source('Ana_Israel_IPM/R/04_IPM_Implementation.R')
source('Ana_Israel_IPM/R/05_Sens_and_Elas.R')
source('Ana_Israel_IPM/R/06_Bootstrap.R')
source('Ana_Israel_IPM/R/07A_Figures_rmd.R')

```


```{r echo = FALSE, warning = FALSE, message = FALSE}
library(kableExtra)
source('Ana_Israel_IPM/R/01_Utility_Functions_and_Dependencies.R')

grow_aic_table <- grow_aic %>%
  as_tibble() %>%
  mutate(Model = "Growth",
         Type  = c("Intercept",
                   "Linear Term Only",
                   "Quadratic Term",
                   "GAM",
                   "Exponential Variance")) %>%
  select(Model, Type, df, AIC) 

surv_aic_table <- surv_aic %>%
  as_tibble() %>%
  mutate(Model = "Survival",
         Type  = c("Intercept",
                   "Linear Term Only",
                   "Quadratic Term",
                   "GAM")) %>%
  select(Model, Type, df, AIC) 

knitr::kable(
  grow_aic_table,
  format = 'latex',
  caption = "Table S1.1: AIC model selection tables for candidate growth models."
) %>%
  column_spec(1, border_left = TRUE) %>%
  column_spec(4, border_right = TRUE)

knitr::kable(
  surv_aic_table,
  format = 'latex',
  caption = "Table S1.2: AIC model selection tables for candidate survival models."
) %>%
  column_spec(1, border_left = TRUE) %>%
  column_spec(4, border_right = TRUE)


```

## IPM Functions

1. $n(z', t + 1) = \int_{L}^{U} K(z',z)n(z, t) dz$

2. $K(z', z) = P(z',z) + F(z', z)$

3. $P(z', z) = s(z) * g(z', z)$

4. $F(z',z)  = p_r(z) * f_s(z) * f_d(z') * f_r$

### P(z',z)

5.  $Logit^{-1}(s(z)) = \beta_{0, s} + \beta_{1,s} * z$

6. $g(z',z) \sim Norm(\mu_g, \sigma_g)$

7.  $\mu_g^{ev} = \beta_{0, g}^{ev} + \beta_{1,g}^{ev} * z$

8. $\sigma_{g}^{ev} = e^{2 * \beta_{\sigma_g} * z}$

9. $\mu_g^{cv} = \beta_{0, g}^{cv} + \beta_{1,g}^{cv} * z$

10. $\sigma_g^{cv} = \sigma_g^{cv}$

### F(z', z)

11.  $Logit^{-1}(p_r(z)) = \beta_{0, p_r} + \beta_{1, p_r} * z$

12.  $ln(f_s(z)) = \beta_{0, f_s} + \beta_{1, f_s} * z$

13. $f_d(z') \sim Norm(\mu_{f_d}, \sigma_{f_d})$
b
### Implementation rules

Integration rule: midpoint

L = `r round(L, 3)`

U = `r round(U, 3)`

*#* meshpoints = 100 
