---
title: "Manuscript Outline"
author: "Sam Levin, Ana Bogdan"
date: "8/2/2019"
output:
  pdf_document: default
---

## Introduction

1. Aizoaceae contains XXX plant species, yet there are no structured demographic studies of any of them. 
    
    + Contains XXX invasive plant species, and XXX rare/endangered species. Structured demographic studies are needed to facilitate syntheses and conservation assessments. 
    
2. Invasions are demoraphic processes whereby spread is determined by biotic, abiotic factors **and** invader vital rates/life history traits (applicable across local and regional scales).
    
    + Carpobrotus spp. are globally invasive and a proper understanding of mechanisms requires a demographic knowledge base. 
    
    + Carpobrotus management can be quite expensive and labor intensive (e.g. manual removal)
    
    + Chemical methods work, but are generally frowned upon
    
    + Finding optimal balance is possible w/ sensitivity/elasticity analysis
    
3. Carpobrotus is difficult to study because it can grow in very inaccesible areas (e.g. cliff sides)

    + Drones make this possible. structure from motion generates 2d maps from 3d data, and state variables can be extracted from these images for use in vital rate regressions.
    
    + drastically reduces the number of personnel needed for sampling, so is cost effective as well. 
    
```{r setup, echo = FALSE}

knitr::opts_knit$set(root.dir = '../../../carpobrotus_IPMs')

```

## Results

```{r echo = FALSE, message = FALSE, include = FALSE, cache = TRUE}

source('Ana_Israel_IPM/R/01_Utility_Functions_and_Dependencies.R')
source('Ana_Israel_IPM/R/02_Read_Data.R')
source('Ana_Israel_IPM/R/03_VR_Model_Selection.R')
source('Ana_Israel_IPM/R/04_IPM_Implementation.R')
source('Ana_Israel_IPM/R/05_Sens_and_Elas.R')
source('Ana_Israel_IPM/R/06_Bootstrap.R')
source('Ana_Israel_IPM/R/07A_Figures_rmd.R')
```

The drones adequately captured population dynamics at resolutions high enough to identify plants and flowers (Appendix 1). 

Vital rate regression using log transformed surface area as a fixed effect yielded good fits for all of our vital rates (Table 1). 

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(kableExtra)

knitr::kable(
  tibble::tribble( ~Parameter, ~Estimated, ~`Lower CI`, ~`Upper CI`,
                  "$\\beta_{0,s}$",  
                  round(const_var_temp$s_int[1], 3),
                  round(const_var_temp$s_int[2], 3),
                  round(const_var_temp$s_int[3], 3),
                
                  "$\\beta_{1,s}$",
                  round(const_var_temp$s_slope[1], 3),
                  round(const_var_temp$s_slope[2], 3),
                  round(const_var_temp$s_slope[3], 3),
                  
                  "$\\beta_{0,g}^{ev}$",
                  round(exp_var_temp$g_int[1], 3),
                  round(exp_var_temp$g_int[2], 3),
                  round(exp_var_temp$g_int[3], 3),
                  
                  "$\\beta_{1,g}^{ev}$",
                  round(exp_var_temp$g_slope[1], 3),
                  round(exp_var_temp$g_slope[2], 3),
                  round(exp_var_temp$g_slope[3], 3),
                  
                  "$\\beta_{0,g}^{cv}$",
                  round(const_var_temp$s_int[1], 3),
                  round(const_var_temp$s_int[2], 3),
                  round(const_var_temp$s_int[3], 3),
                  
                  "$\\beta_{1, g}^{cv}$",
                  round(const_var_temp$g_slope[1], 3),
                  round(const_var_temp$g_slope[2], 3),
                  round(const_var_temp$g_slope[3], 3),
                  
                  "$\\beta_{\\sigma_g}$",
                  round(exp_var_temp$g_sigma_par[1], 3),
                  round(exp_var_temp$g_sigma_par[2], 3), 
                  round(exp_var_temp$g_sigma_par[3], 3),
                  
                  "$\\sigma_g^{cv}$",
                  round(const_var_temp$sd_g[1], 3),
                  round(const_var_temp$sd_g[2], 3),
                  round(const_var_temp$sd_g[3], 3),
                  
                  "$\\beta_{0, p_r}$",
                  round(const_var_temp$p_r_int[1], 3),
                  round(const_var_temp$p_r_int[2], 3),
                  round(const_var_temp$p_r_int[3], 3),
                  
                  "$\\beta_{1, p_r}$",
                  round(const_var_temp$p_r_slope[1], 3),
                  round(const_var_temp$p_r_slope[2], 3),
                  round(const_var_temp$p_r_slope[3], 3),
                  
                  "$\\beta_{0, f_s}$",
                  round(const_var_temp$f_s_int[1], 3),
                  round(const_var_temp$f_s_int[2], 3),
                  round(const_var_temp$f_s_int[3], 3),
                  
                  "$\\beta_{1, f_s}$",
                  round(const_var_temp$f_s_slope[1], 3),
                  round(const_var_temp$f_s_slope[2], 3), 
                  round(const_var_temp$f_s_slope[3], 3),
                  
                  "$\\mu_{f_d}$",
                  round(const_var_temp$f_d_mu[1], 3),
                  round(const_var_temp$f_d_mu[2], 3),
                  round(const_var_temp$f_d_mu[3], 3),
                  
                  "$\\sigma_{f_d}$",
                  round(const_var_temp$f_d_sd[1], 3),
                  round(const_var_temp$f_d_sd[2], 3),
                  round(const_var_temp$f_d_sd[3], 3)
  ),
format = 'latex',
escape = FALSE,
caption = "Table 1: Estimated regression coefficients and their 95% confidence intervals. Confidence intervals were obtained by bootstrapping the data set 1000 times and re-fitting the model."
) %>%
  column_spec(1, border_left = TRUE) %>%
  column_spec(4, border_right = TRUE)
```

$\lambda_{cv}$ = `r round(const_var_temp$lambda[1], 3)`  (Lower CI = `r round(const_var_temp$lambda[2], 3)`, Upper CI = `r round(const_var_temp$lambda[3], 3)`) and $\lambda_{ev}$  = `r round(exp_var_temp$lambda[1], 3)`  (Lower CI = `r round(exp_var_temp$lambda[2], 3)`, Upper CI = `r round(exp_var_temp$lambda[3], 3)`). In both cases, the point estimate of population growth rate is below 1, indicating shrinking populations. However, the exponential variance model's confidence intervals include 1, indicating that the population may well be stable or growing. The constant variance model predicts a declining population in all cases. Elasticity analysis concluded that survival/growth transitions are far more important to $\lambda$ regardless of the model, though the exponential variance model predicted slightly less importance than the constant variance model (Figure 2).

