---
title: "Manuscript Outline"
author: "Sam Levin, Ana Bogdan"
date: "8/2/2019"
output:
  word_document: default
---

## Introduction

1. Aizoaceae contains XXX plant species, yet there are no structured demographic studies of any of them. 
    
    + Contains XXX invasive plant species, and XXX rare/endangered species. Structured demographic studies are needed to facilitate syntheses and conservation assessments. 
    
2. Invasions are demoraphic processes whereby spread is determined by biotic, abiotic factors **and** invader vital rates/life history traits (applicable across local and regional scales).
    
    + Carpobrotus spp. are globally invasive and a proper understanding of mechanisms requires a demographic knowledge base. 
    
    + Carpobrotus management can be quite expensive and labor intensive (e.g. manual removal)
    
    + Chemical methods work, but are generally frowned upon
    
    + Finding optimal balance is possible w/ sensitivity/elasticity analysis
    
3. Carpobrotus is difficult to study because it can grow in very inaccesible areas (e.g. cliff sides)

    + Drones make this possible. structure from motion generates 2d maps from 3d data, and state variables can be extracted from these images for use in vital rate regressions.
    
    + drastically reduces the number of personnel needed for sampling, so is cost effective as well. 
    
```{r setup, echo = FALSE}

knitr::opts_knit$set(root.dir = '../../../carpobrotus_IPMs')

```

## Results

```{r echo = FALSE, message = FALSE, include = FALSE, cache = TRUE}

source('Ana_Israel_IPM/R/01_Utility_Functions_and_Dependencies.R')
source('Ana_Israel_IPM/R/02_Read_Data.R')
source('Ana_Israel_IPM/R/03_VR_Model_Selection.R')
source('Ana_Israel_IPM/R/04_IPM_Implementation.R')
source('Ana_Israel_IPM/R/05_Sens_and_Elas.R')
source('Ana_Israel_IPM/R/06_Bootstrap.R')
source('Ana_Israel_IPM/R/07A_Figures_rmd.R')
```

The drone flights were successful, generating ultra-high resolution orthomosaic maps of approximately 2.3 hectares for the population in each year. 85% image overlap (front and side) provided an excellent balance between quality and speed, with neither site taking more than 2 hours of total time in the field to survey. The technique of overlaying maps from subsequent years adequately captured population dynamics at resolutions high enough to identify plants and flowers (Appendix 1). We identified `r dim(data_t_1)[1]` distinct ramets in 2018, re-found `r sum(all_data$survival, na.rm = TRUE)`, and were able to mark `r dim(recruit_t_2)[1]` new individuals. Georeferencing accuracy varied throughout the orthomosaic due to the blocks generated in 2018, but was never off by more than 4m, and we are confident that we correctly identified each ramet in 2019 as either existing or new. 

Vital rate regression using log transformed surface area as a fixed effect yielded good fits for all of our vital rates and generally lower AIC scores than intercept-only, quadratic fits, or GAMS (Figure 2, Table 1, Appendix 1). We found that GAMs and polynomial fits didn't substantially improve the overall model fit or substantially lower the AIC score for each vital rate, even with the increased complexity of the model itself. Thus, our IPM only includes models with a single fixed effect - log transformed surface area - as explanatory variables (Appendix 1). 

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(kableExtra)

options(knitr.kable.NA = "")

knitr::kable(
  tibble::tribble( ~Parameter, ~Estimated, ~`Lower CI`, ~`Upper CI`, ~`Sample Size`,
                  "$\\beta_{0,s}$",  
                  round(exp_var_temp$s_int[1], 3),
                  round(exp_var_temp$s_int[2], 3),
                  round(exp_var_temp$s_int[3], 3),
                  sum(!is.na(all_data$survival)),
                  
                
                  "$\\beta_{1,s}$",
                  round(exp_var_temp$s_slope[1], 3),
                  round(exp_var_temp$s_slope[2], 3),
                  round(exp_var_temp$s_slope[3], 3),
                  NA_real_,
                  
                  "$\\beta_{0,g}$",
                  round(exp_var_temp$g_int[1], 3),
                  round(exp_var_temp$g_int[2], 3),
                  round(exp_var_temp$g_int[3], 3),
                  sum(all_data$survival, na.rm = TRUE),
                  
                  "$\\beta_{1,g}$",
                  round(exp_var_temp$g_slope[1], 3),
                  round(exp_var_temp$g_slope[2], 3),
                  round(exp_var_temp$g_slope[3], 3),
                  NA_real_,
                 
                  "$\\beta_{\\sigma_g}$",
                  round(exp_var_temp$g_sigma_par[1], 3),
                  round(exp_var_temp$g_sigma_par[2], 3), 
                  round(exp_var_temp$g_sigma_par[3], 3),
                  NA_real_,
                  
                  "$\\beta_{0, p_r}$",
                  round(exp_var_temp$p_r_int[1], 3),
                  round(exp_var_temp$p_r_int[2], 3),
                  round(exp_var_temp$p_r_int[3], 3),
                  sum(!is.na(all_data$survival)),

                  "$\\beta_{1, p_r}$",
                  round(exp_var_temp$p_r_slope[1], 3),
                  round(exp_var_temp$p_r_slope[2], 3),
                  round(exp_var_temp$p_r_slope[3], 3),
                  NA_real_,
                  
                  "$\\beta_{0, f_s}$",
                  round(exp_var_temp$f_s_int[1], 3),
                  round(exp_var_temp$f_s_int[2], 3),
                  round(exp_var_temp$f_s_int[3], 3),
                  sum(all_data$repro, na.rm = TRUE),
                  
                  "$\\beta_{1, f_s}$",
                  round(exp_var_temp$f_s_slope[1], 3),
                  round(exp_var_temp$f_s_slope[2], 3), 
                  round(exp_var_temp$f_s_slope[3], 3),
                  NA_real_,
                  
                  "$\\mu_{f_d}$",
                  round(exp_var_temp$f_d_mu[1], 3),
                  round(exp_var_temp$f_d_mu[2], 3),
                  round(exp_var_temp$f_d_mu[3], 3),
                  dim(recruit_t_2)[1],
                  
                  "$\\sigma_{f_d}$",
                  round(exp_var_temp$f_d_sd[1], 3),
                  round(exp_var_temp$f_d_sd[2], 3),
                  round(exp_var_temp$f_d_sd[3], 3),
                  dim(recruit_t_2)[1],
                  
                  "$\\lambda$",
                  round(exp_var_temp$lambda[1], 3),
                  round(exp_var_temp$lambda[2], 3),
                  round(exp_var_temp$lambda[3], 3),
                  NA_real_
  ),
format = 'pandoc',
escape = FALSE,
caption = "Table 1: Estimated regression coefficients and their 95% confidence intervals. Confidence intervals were obtained by bootstrapping the data set 1000 times and re-fitting the model."
) %>%
  column_spec(1, border_left = TRUE) %>%
  column_spec(4, border_right = TRUE)
```

Our point estimage of $\lambda$  is `r round(exp_var_temp$lambda[1], 3)`  (Lower CI = `r round(exp_var_temp$lambda[2], 3)`, Upper CI = `r round(exp_var_temp$lambda[3], 3)`). The point estimate of population growth rate is below 1, indicating shrinking populations. However, the model's confidence intervals include 1, indicating that the population may well be stable or growing (Figure 2). Elasticity analysis concluded that survival/growth transitions are far more important to $\lambda$ regardless of the model (Figure 3).

