---
title: "flower_n" 
output:
  html_document:
    toc: true
---

# Summary

All of the interaction models are basically indistinguishable. Only one not in WAIC marign of error is sw3_ann. All positive size coefficients. Interestingly, in this model, those do not seem to have the largest effect size, though are far more certain.


## sw3_seas

prec_wet and sw3_dry are very close to non-0 and point estimates are `---`. All interactions are non-0 and `-`, except for temp_wet and sw3_wet which are `+`.

## sw1_seas

no non-0 non-interaction coefs. for interactions, prec_dry_t_1 is `-`, sw1_dry_t_1 is `+`, and sw1_wet_t_1 is `-`. 

## sw2_ann 

no non-0 non-interactio coefs. log_size:mean_temp_t_1 (`-`), log_size:seas_prec_t_1 (`+`), log_size:mean_sw2_t_1 (`-`), log_size:seas_sw2_t_1 (`-`). 

## sw1_ann

no non-0 non-interaction coefs. for interactions, mean_temp_t_1 is `-`, seas_prec_t_1 is `+`, mean and seas sw1 are `-`. 

## sw3_ann

no non-0 non-interaction coefs. for interactions  log_size:mean_temp_t_1 is `-`, seas_temp_t_1 is `-`, total_prec_t_1 is `-`, mean_sw3_t_1 is `-`.

## Seasonal models 

Seems that there are conflicting notions of what happens w/ sw1 and sw3. I am not sure what to make of this, except wait and see what happens w/ the GAMS.

## Annual models

Overall, there is a consistent trend for mean temp X size (`-`), and mean soil water X size (`-`). The others are hit or miss, though seas_prec seems positive or close to positive. 

# All Results 

```{r echo = FALSE}

 mod_list <- readRDS('../../Model_Fits/ramet_flower_n_list_krig.rds') 
```

## WAIC Results

```{r echo = FALSE}

 print(mod_list[[1]]$mod_waic.diffs) 

```

##  native_only   



```{r echo = FALSE}

 summary(mod_list[[1]][[1]], prob = 0.89) 

 plot(mod_list[[1]][[1]], ask = FALSE)
 pp_check(mod_list[[1]][[1]],
type   = 'scatter_avg_grouped',
group  = 'site',
ndraws = 100L) 

```



##  add_sw1_seas   



```{r echo = FALSE}

 summary(mod_list[[1]][[2]], prob = 0.89) 

 plot(mod_list[[1]][[2]], ask = FALSE)
 pp_check(mod_list[[1]][[2]],
type   = 'scatter_avg_grouped',
group  = 'site',
ndraws = 100L) 

```



##  times_sw1_seas   



```{r echo = FALSE}

 summary(mod_list[[1]][[3]], prob = 0.89) 

 plot(mod_list[[1]][[3]], ask = FALSE)
 pp_check(mod_list[[1]][[3]],
type   = 'scatter_avg_grouped',
group  = 'site',
ndraws = 100L) 

```



##  add_sw2_seas   



```{r echo = FALSE}

 summary(mod_list[[1]][[4]], prob = 0.89) 

 plot(mod_list[[1]][[4]], ask = FALSE)
 pp_check(mod_list[[1]][[4]],
type   = 'scatter_avg_grouped',
group  = 'site',
ndraws = 100L) 

```



##  times_sw2_seas   



```{r echo = FALSE}

 summary(mod_list[[1]][[5]], prob = 0.89) 

 plot(mod_list[[1]][[5]], ask = FALSE)
 pp_check(mod_list[[1]][[5]],
type   = 'scatter_avg_grouped',
group  = 'site',
ndraws = 100L) 

```



##  add_Sw3_seas   



```{r echo = FALSE}

 summary(mod_list[[1]][[6]], prob = 0.89) 

 plot(mod_list[[1]][[6]], ask = FALSE)
 pp_check(mod_list[[1]][[6]],
type   = 'scatter_avg_grouped',
group  = 'site',
ndraws = 100L) 

```



##  times_sw3_seas   



```{r echo = FALSE}

 summary(mod_list[[1]][[7]], prob = 0.89) 

 plot(mod_list[[1]][[7]], ask = FALSE)
 pp_check(mod_list[[1]][[7]],
type   = 'scatter_avg_grouped',
group  = 'site',
ndraws = 100L) 

```



##  add_sw1_ann   



```{r echo = FALSE}

 summary(mod_list[[1]][[8]], prob = 0.89) 

 plot(mod_list[[1]][[8]], ask = FALSE)
 pp_check(mod_list[[1]][[8]],
type   = 'scatter_avg_grouped',
group  = 'site',
ndraws = 100L) 

```



##  times_sw1_ann   



```{r echo = FALSE}

 summary(mod_list[[1]][[9]], prob = 0.89) 

 plot(mod_list[[1]][[9]], ask = FALSE)
 pp_check(mod_list[[1]][[9]],
type   = 'scatter_avg_grouped',
group  = 'site',
ndraws = 100L) 

```



##  add_sw2_ann   



```{r echo = FALSE}

 summary(mod_list[[1]][[10]], prob = 0.89) 

 plot(mod_list[[1]][[10]], ask = FALSE)
 pp_check(mod_list[[1]][[10]],
type   = 'scatter_avg_grouped',
group  = 'site',
ndraws = 100L) 

```



##  times_sw2_ann   



```{r echo = FALSE}

 summary(mod_list[[1]][[11]], prob = 0.89) 

 plot(mod_list[[1]][[11]], ask = FALSE)
 pp_check(mod_list[[1]][[11]],
type   = 'scatter_avg_grouped',
group  = 'site',
ndraws = 100L) 

```



##  add_Sw3_ann   



```{r echo = FALSE}

 summary(mod_list[[1]][[12]], prob = 0.89) 

 plot(mod_list[[1]][[12]], ask = FALSE)
 pp_check(mod_list[[1]][[12]],
type   = 'scatter_avg_grouped',
group  = 'site',
ndraws = 100L) 

```



##  times_sw3_ann   



```{r echo = FALSE}

 summary(mod_list[[1]][[13]], prob = 0.89) 

 plot(mod_list[[1]][[13]], ask = FALSE)
 pp_check(mod_list[[1]][[13]],
type   = 'scatter_avg_grouped',
group  = 'site',
ndraws = 100L) 

```

